Improving the Replicability of Psychological Science Through Pedagogy

### 2017-07-24 paper/paper.Rmd
super minor tweak to sample size

Still, collecting sufficiently large samples through AMT may strain financial resources. Depending on the number of target studies, the needs of those studies, the level of the student group, and the total funds allocated to the course (e.g. through teaching grants or departmental support), other populations may be more feasible and appropriate. For instance, recruitment from community samples or university participant pools may provide high-quality data while reducing costs and eliminating a major technical component of the workflow.

>>>>

Still, collecting sufficiently large samples through AMT may strain financial resources. Depending on the number of target studies, the needs of those studies, the level of the student group, and the total funds allocated to the course (e.g., through teaching grants or departmental support), other populations may be more feasible and appropriate. For instance, recruitment from community samples or university participant pools may provide high-quality data while reducing costs and eliminating a technical challenge in data collection.
